### 2020-08-24 benchmarking/benchmarkingVM/ESS_round1_catquant.tex
results update

% Created by tikzDevice version 0.12.3 on 2020-08-10 13:51:28
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}
\usepackage[active,tightpage,psfixbb]{preview}
\PreviewEnvironment{pgfpicture}
\setlength\PreviewBorder{0pt}
\usepackage{amssymb}\begin{document}

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,301.03) {ESS/hr [nocons (\textit{quant})]};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,433.62) {ESS/hr [cons (\textit{quant})]};
\end{scope}
\begin{scope}
\path[clip] ( 49.80,338.88) rectangle (239.28,528.36);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00,374.64) --
	(203.52,578.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (286.65,578.16) --
	(286.65,490.17) --
	(  0.00,203.52);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (  0.00,346.12) --
	(232.04,578.16);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (286.65,578.16) --
	(286.65,518.69) --
	(  0.00,232.04);

\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (  0.00,317.60) --
	(260.56,578.16);

\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (286.65,578.16) --
	(286.65,547.21) --
	(  0.00,260.56);

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (142.89,342.31) {$\frac{1}{64} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,435.87) {$64\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (114.37,342.31) {$\frac{1}{16} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,407.35) {$16\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 84.20,342.31) {$\frac{1}{4} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92,378.83) {$4\times$};

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 94.65,416.78) --
	(103.65,416.78);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.64,409.37) --
	( 99.64,422.22);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 99.64,413.56) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (186.25,476.46) --
	(190.95,476.46);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (188.73,475.74) --
	(188.73,477.16);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (188.73,472.43) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (100.21,474.21) --
	(104.27,474.21);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (102.34,473.61) --
	(102.34,474.79);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (102.34,470.18) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.11,416.10) --
	(103.73,416.10);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.87,410.35) --
	( 99.87,420.59);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 99.87,412.07) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 89.40,387.89) --
	(115.90,387.89);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (106.65,384.62) --
	(106.65,390.72);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (106.65,384.99) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.54,483.66) --
	(195.01,483.66);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.29,483.25) --
	(194.29,484.06);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.29,480.76) {$\kappa$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (145.24,453.03) --
	(151.45,453.03);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (148.58,451.65) --
	(148.58,454.32);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (148.58,449.80) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.12,479.26) --
	(197.83,479.26);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.99,477.50) --
	(196.99,480.89);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.99,475.23) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.36,483.73) --
	(188.58,483.73);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.98,483.50) --
	(187.98,483.96);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.98,479.70) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (138.83,449.81) --
	(142.53,449.81);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.76,448.18) --
	(140.76,451.31);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (140.76,445.77) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (145.30,448.54) --
	(152.66,448.54);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (149.31,447.26) --
	(149.31,449.74);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (149.31,445.63) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.59,488.02) --
	(199.40,488.02);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (199.00,487.58) --
	(199.00,488.46);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.00,485.12) {$\kappa$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (117.84,422.09) --
	(126.52,422.09);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (122.64,409.09) --
	(122.64,429.99);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (122.64,418.86) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (191.62,458.97) --
	(195.24,458.97);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.51,454.93) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (162.66,477.15) --
	(163.23,477.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (162.95,476.14) --
	(162.95,478.11);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (162.95,473.11) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (112.91,421.56) --
	(120.70,421.56);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (117.17,406.76) --
	(117.17,430.08);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (117.17,417.53) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (124.20,409.98) --
	(134.18,409.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (129.79,405.95) --
	(129.79,413.35);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (129.79,407.07) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.21,485.10) --
	(197.03,485.10);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.62,484.28) --
	(196.62,485.89);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.62,482.19) {$\kappa$};
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (129.77,432.05) --
	(140.26,432.05);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (135.68,429.18) --
	(135.68,434.57);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (135.68,428.82) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.99,483.34) --
	(200.70,483.34);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (199.86,480.63) --
	(199.86,485.72);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.86,479.30) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.36,482.25) --
	(177.58,482.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.47,482.07) --
	(177.47,482.44);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (177.47,478.22) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (133.12,451.72) --
	(147.88,451.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (141.79,449.82) --
	(141.79,453.46);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (141.79,447.69) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (136.74,437.84) --
	(147.60,437.84);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (142.88,434.82) --
	(142.88,440.47);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (142.88,434.94) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.27,487.58) --
	(198.98,487.58);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.14,487.05) --
	(198.14,488.10);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (198.14,484.68) {$\kappa$};
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.42,460.68) --
	(181.15,460.68);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (179.37,456.94) --
	(179.37,463.84);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (179.37,457.45) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (162.94,486.46) --
	(184.37,486.46);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (176.33,482.75) --
	(176.33,489.60);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (176.33,482.42) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.15,482.18) --
	(197.23,482.18);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.69,481.57) --
	(196.69,482.78);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.69,478.15) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (153.45,441.52) --
	(161.00,441.52);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (157.57,436.94) --
	(157.57,445.26);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (157.57,437.48) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (179.01,463.73) --
	(184.30,463.73);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.82,459.32) --
	(181.82,467.36);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (181.82,460.82) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (208.90,498.16) --
	(211.56,498.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (210.27,495.77) --
	(210.27,500.30);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.27,495.25) {$\kappa$};
\definecolor{drawColor}{RGB}{68,68,68}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (191.64,472.51) --
	(197.79,472.51);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.95,470.68) --
	(194.95,474.19);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.95,469.28) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (174.60,491.62) --
	(178.99,491.62);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (176.91,490.07) --
	(176.91,493.06);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (176.91,487.58) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.25,482.68) --
	(197.61,482.68);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.43,482.27) --
	(197.43,483.09);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.43,478.65) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (175.17,459.25) --
	(178.40,459.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (176.85,457.81) --
	(176.85,460.59);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (176.85,455.21) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (173.79,467.29) --
	(192.74,467.29);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (185.37,464.24) --
	(185.37,469.95);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.37,464.39) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.72,501.36) --
	(212.84,501.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.78,500.78) --
	(212.78,501.94);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (212.78,498.46) {$\kappa$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,338.88) -- (239.28,338.88);

>>>>

% Created by tikzDevice version 0.12.3.1 on 2020-08-24 19:04:32
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}
\usepackage[active,tightpage,psfixbb]{preview}
\PreviewEnvironment{pgfpicture}
\setlength\PreviewBorder{0pt}
\usepackage{amssymb}\begin{document}

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,301.03) {ESS/chain [nocons (\textit{quant})]};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,433.62) {ESS/chain [cons (\textit{quant})]};
\end{scope}
\begin{scope}
\path[clip] ( 49.80,338.88) rectangle (239.28,528.36);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00,368.65) --
	(209.51,578.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (283.33,578.16) --
	(283.33,492.84) --
	(  0.00,209.51);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (  0.00,342.13) --
	(236.03,578.16);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (283.33,578.16) --
	(283.33,519.37) --
	(  0.00,236.03);

\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (  0.00,315.60) --
	(262.56,578.16);

\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (283.33,578.16) --
	(283.33,545.89) --
	(  0.00,262.56);

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (136.90,342.31) {$\frac{1}{64} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,429.88) {$64\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (110.38,342.31) {$\frac{1}{16} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,403.36) {$16\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 82.20,342.31) {$\frac{1}{4} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92,376.84) {$4\times$};

@@

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (146.55,466.16) --
	(158.29,466.16);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (153.31,462.75) --
	(153.31,469.06);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (153.31,462.93) {$p$};
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.24,515.97) --
	(190.72,515.97);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.95,514.61) --
	(186.95,517.24);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (186.95,511.94) {$L$};
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (141.27,507.51) --
	(146.34,507.51);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (143.97,507.30) --
	(143.97,507.72);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (143.97,503.48) {$r$};
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (141.32,461.89) --
	(150.41,461.89);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (146.40,454.67) --
	(146.40,467.11);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (146.40,457.85) {$h$};
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (107.73,439.48) --
	(121.71,439.48);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (115.97,429.54) --
	(115.97,445.99);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (115.97,436.58) {$\sigma$};
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (224.56,513.60) --
	(225.34,513.60);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (224.96,513.22) --
	(224.96,513.97);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (224.96,510.69) {$\kappa$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (212.80,499.16) --
	(214.49,499.16);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (213.66,497.99) --
	(213.66,500.27);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (213.66,495.94) {$p$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.38,483.91) --
	(193.63,483.91);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (193.01,482.28) --
	(193.01,485.40);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.01,479.87) {$L$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (219.89,514.97) --
	(220.35,514.97);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (220.12,514.79) --
	(220.12,515.14);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (220.12,510.93) {$r$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (203.60,494.30) --
	(207.53,494.30);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (205.67,493.23) --
	(205.67,495.31);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (205.67,490.27) {$h$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (214.64,497.73) --
	(216.55,497.73);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (215.62,496.54) --
	(215.62,498.85);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (215.62,494.83) {$\sigma$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (224.49,514.56) --
	(225.65,514.56);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (225.08,514.02) --
	(225.08,515.09);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (225.08,511.66) {$\kappa$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (170.28,470.40) --
	(175.14,470.40);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.86,468.37) --
	(172.86,472.24);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (172.86,467.18) {$p$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (201.34,496.33) --
	(204.09,496.33);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (202.76,494.98) --
	(202.76,497.58);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (202.76,492.29) {$L$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (223.55,516.52) --
	(224.53,516.52);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (224.05,516.26) --
	(224.05,516.77);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (224.05,512.48) {$r$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (159.45,457.17) --
	(165.46,457.17);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (162.69,454.81) --
	(162.69,459.28);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (162.69,453.14) {$h$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (180.00,474.69) --
	(190.72,474.69);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.11,471.18) --
	(186.11,477.64);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (186.11,471.78) {$\sigma$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (227.77,516.29) --
	(228.21,516.29);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (227.99,515.94) --
	(227.99,516.64);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (227.99,513.39) {$\kappa$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.06,489.34) --
	(190.32,489.34);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.76,488.63) --
	(188.76,490.02);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (188.76,486.11) {$p$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.99,489.04) --
	(194.37,489.04);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.31,486.77) --
	(192.31,491.07);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.31,485.01) {$L$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (218.80,514.30) --
	(219.31,514.30);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (219.06,514.16) --
	(219.06,514.43);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (219.06,510.26) {$r$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (175.50,485.31) --
	(182.06,485.31);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.06,483.39) --
	(179.06,487.05);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (179.06,481.27) {$h$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (178.00,481.50) --
	(186.35,481.50);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.63,479.81) --
	(182.63,483.06);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (182.63,478.60) {$\sigma$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (227.74,516.74) --
	(228.17,516.74);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (227.96,516.39) --
	(227.96,517.08);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (227.96,513.84) {$\kappa$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (162.10,466.73) --
	(168.36,466.73);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (165.49,463.57) --
	(165.49,469.44);
\definecolor{drawColor}{RGB}{0,219,171}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (165.49,463.50) {$p$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (198.81,509.25) --
	(205.39,509.25);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (202.39,507.51) --
	(202.39,510.84);
\definecolor{drawColor}{RGB}{0,219,171}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (202.39,505.21) {$L$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (197.30,509.61) --
	(198.11,509.61);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (197.71,509.14) --
	(197.71,510.08);
\definecolor{drawColor}{RGB}{0,219,171}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.71,505.58) {$r$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (153.88,467.30) --
	(166.55,467.30);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (161.25,464.25) --
	(161.25,469.93);
\definecolor{drawColor}{RGB}{0,219,171}
